Articles of Association of London Hackspace Ltd.

### 2011-07-21 constitution/articles-body.tex
Remove placeholder for directors majority

\item
  \begin{enumerate}
    \item
    Decisions of the directors may be made either:
    \begin{enumerate}
        \item
        by the use of the Governance System; or
        \item
        by a written resolution in accordance with the procedure described below.
    \end{enumerate}
    \item
    All directors' decisions must be made in one of these two ways, and a decision
    made in any other way will be ineffective.
    \item
    The requisite number of directors who must accept a proposal made using the
    Governance System or a written resolution before it is passed is [a majority of the
    number of directors for the time being].
  \end{enumerate}

>>>>

\item
  \begin{enumerate}
    \item
    Decisions of the directors may be made either:
    \begin{enumerate}
        \item
        by the use of the Governance System; or
        \item
        by a written resolution in accordance with the procedure described below.
    \end{enumerate}
    \item
    All directors' decisions must be made in one of these two ways, and a decision
    made in any other way will be ineffective.
    \item
    A majority of the directors must accept a proposal made using the
    Governance System or a written resolution before it is passed.
  \end{enumerate}
